---
title: "Fine Mapping"
output: 
  html_document:
      toc: true
      toc_float: true
      toc_depth: 3
date: 4/27/2027
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = TRUE)

library(here)
library(tidyverse)
library(patchwork)
library(stargazer)
library(ggcorrplot)
library(gt) 
library(gtsummary)
library(viridis)
library(paletteer)
library(survival)
theme_set(theme_light())
options(dplyr.summarise.inform=F)
col1 = "#F06719FF"; col2 = "#1BA3C6FF"
col1a = "#7873C0FF"; col2a = "#21B087FF"; col3 = "#F06719FF";col4 = "#1BA3C6FF"; col5 = "#F64971FF"; col6= "#F8B620FF"
source(here::here("code", "utilities.R"))
source(here::here("code", "prep_data.R"))

meds = read_csv(here::here("data", "processed", "vasopressor-inotrope-dose.csv")) %>% 
  mutate(ID = as.character(ID))

# covariates data frame 
df = 
  map_ci %>% 
  filter(id %in% wake_covars$id) %>% 
  magrittr::set_colnames(c("id", "hypo_q1", "hypo_q2", "hypo_q3", "hypo_q4",
                           "normo_q1", "normo_q2", "normo_q3", "normo_q4")) %>% 
  left_join(wake_covars) %>% 
  select(-contains("hypo"), -contains("normo")) %>% 
  left_join(meds %>% rename(vis_score = total, id = ID))


mapping_cihigh = read_rds(here::here("data", "analysis", "all_ranges_hici.rds"))
mapping_cilow = read_rds(here::here("data", "analysis", "all_ranges_lowci.rds"))
mapping = read_rds(here::here("data", "analysis", "all_ranges.rds"))

# physiological zones 
pzones = read_rds(here::here("data", "analysis", "pzones.rds"))
pzones_low = read_rds(here::here("data", "analysis", "pzones_lowci.rds"))
pzones_hi = read_rds(here::here("data", "analysis", "pzones_hici.rds"))


map_order = mapping %>% select(starts_with("map") & !contains("cvp")) %>% colnames
map_order2 = mapping %>% select(starts_with("map") & !contains("cvp")) %>% colnames %>% 
  sub(".*map\\_", "", .)

cvp_order = mapping %>% select(starts_with("cvp") & !contains("map")) %>% colnames
cvp_order2 = mapping %>% select(starts_with("cvp") & !contains("map")) %>% colnames %>% 
  sub(".*cvp\\_", "", .)

map_order3 = c("[45,55]", "(55,65]", "(65,75]", "(75,85]",
               "(85,95]", "(95,105]", "(105,115]")

covars_control = df %>% 
  select(cat_gender,
    val_creatlst,
    val_age,
    val_bmi,
    bin_htn,
    bin_diabetes,
    bin_stroke,
    bin_ef40,
    bin_mi,
    bin_chf,
    bin_pvd,
    bin_cld,
    bin_betablocker,
    bin_acearb,
    bin_statin,
    bin_redo,
    bin_emergent,
    val_crystalloid,
    val_cpbtime,
    cat_rbc,
    val_hematocrit,
    vis_score) %>% colnames()

aki_ids = df %>% filter(bin_aki48h == 1) %>% pull(id)

# read in 
```

**For all of the below analysis, I am excluding intra-CPB** 

### Table One 

```{r table one}
tableone::CreateTableOne(data = df,
                         strata = "bin_aki48h",
                         vars = covars_control)

```

### Hemodynamics EDA 

Median CVP measurement is ~12, Q1 and Q3 are 8 and 15, respectively 

```{r dists}
hemo %>% 
  filter(cat_cpb != "intra") %>% 
  ggplot(aes(x = val_cvp)) +
  geom_histogram(binwidth = 1, color = "black", fill = col2a) +
  labs(x = "CVP", y = "Count of Measurements") +
  scale_x_continuous(breaks = seq(0, 26, 2))

hemo %>% 
  filter(cat_cpb != "intra") %>% 
  ggplot(aes(x = val_cvp)) +
  geom_boxplot() +
  labs(x = "CVP", y = "") +
  scale_x_continuous(breaks = seq(0, 26, 2)) +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

hemo %>% 
  filter(cat_cpb != "intra") %>% 
  ggplot(aes(x = val_map)) +
  geom_histogram(binwidth = 5, color = "black", fill = col2a) +
  labs(x = "MAP", y = "Count of Measurements") +
  scale_x_continuous(breaks=seq(0,250,25))

hemo %>% 
  filter(cat_cpb != "intra") %>% 
  ggplot(aes(x = val_map)) +
  geom_boxplot() +
  labs(x = "MAP", y = "") +
  scale_x_continuous(breaks=seq(0,250,25)) +
   theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

hemo %>% 
  filter(cat_cpb != "intra") %>% 
  ggplot(aes(x = val_ci)) +
  geom_histogram(binwidth = .5, color = "black", fill = col2a) +
  labs(x = "CI", y = "Count of Measurements") +
  scale_x_continuous(breaks=seq(0, 20, .5))

hemo %>% 
  filter(cat_cpb != "intra") %>% 
  ggplot(aes(x = val_ci)) +
  geom_boxplot() +
  labs(x = "CI", y = "") +
  scale_x_continuous(breaks=seq(0, 20, .5)) +
   theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank())
```

#### Comparison with JHU cohort 2016-2019 

```{r compare to jhu}
jhu_data = read_rds(here::here("..", "fine_mapping",
                               "data", "analytic", 
                               "hemo_timeseries_interp_post_exclusion.rds")) %>% 
  filter(cat_cpb != "intra" & cat_anes == "intra") %>% 
  janitor::clean_names()

joined = 
  jhu_data %>% 
  mutate(cohort = "jhu") %>% 
  bind_rows(hemo %>% 
  filter(cat_cpb != "intra") %>% 
    mutate(cohort = "wake")) 

joined %>% 
  ggplot(aes(x = val_cvp)) +
  geom_histogram(binwidth = 1, color = "black") +
  facet_grid(cohort ~ ., scales = "free_y") +
  labs(x = "CVP", y = "Count of measurements") +
  scale_x_continuous(breaks = seq(0, 26, 2))

joined %>% 
  ggplot(aes(x = cohort, y = val_cvp)) +
  geom_boxplot() +
  labs(x = "Cohort", y = "CVP") +
  scale_y_continuous(breaks = seq(0, 26, 2))

```


```{r compare to jhu map}

joined %>% 
  ggplot(aes(x = val_map)) +
  geom_histogram(binwidth = 5, color = "black") +
  facet_grid(cohort ~ ., scales = "free_y") +
  labs(x = "MAP", y = "Count of measurements") 
  # scale_x_continuous(breaks = seq(0, 26, 2))

joined %>% 
  ggplot(aes(x = cohort, y = val_map)) +
  geom_boxplot(outlier.alpha = .05, outlier.size = .4) +
  labs(x = "Cohort", y = "MAP") +
  scale_y_continuous(breaks=seq(25, 250, 25))
```

### Amount of Data in Ranges {.tabset}

#### MAP 

```{r map heatmap}
mapping %>% 
  select(id, (starts_with("map") & !contains("cvp"))) %>% 
  pivot_longer(cols = -id) %>% 
  group_by(name) %>% 
  summarize(n = n(), 
            across(value, .fns = list(mean = mean, sd = sd)),
            .groups = "drop") %>% 
  mutate(value_se = value_sd / sqrt(n),
         lb = value_mean - 1.96 * value_se, 
         ub = value_mean + 1.96 * value_se) %>% 
  mutate(name = sub(".*map\\_", "", name)) %>% 
  mutate(name = factor(name, levels = map_order2)) %>% 
  ggplot(aes(x = name, y = value_mean)) +
  geom_point(size = 2) + 
  geom_errorbar(aes(ymin = lb, ymax = ub), width = .25, linewidth = 1.1) +
  # scale_color_viridis() +
  theme(legend.position = "none") +
  labs(x = "MAP", y = "Minutes", title = "Mean (95% CI) Minutes Spent in Range") +
  scale_y_continuous(breaks = seq(0, 30, 5))

xlow = 
  mapping_cilow %>% 
  select(id, (starts_with("map") & !contains("cvp"))) %>% 
  pivot_longer(cols = -id) %>% 
  group_by(name) %>% 
  summarize(n = n(), 
            across(value, .fns = list(mean = mean, sd = sd)),
            .groups = "drop") %>% 
  mutate(value_se = value_sd / sqrt(n),
         lb = value_mean - 1.96 * value_se, 
         ub = value_mean + 1.96 * value_se) %>% 
  mutate(name = sub(".*map\\_", "", name)) %>% 
  mutate(name = factor(name, levels = map_order2)) %>% 
  mutate(type = "low")

xhi = 
  mapping_cihigh %>% 
  select(id, (starts_with("map") & !contains("cvp"))) %>% 
  pivot_longer(cols = -id) %>% 
  group_by(name) %>% 
  summarize(n = n(), 
            across(value, .fns = list(mean = mean, sd = sd)),
            .groups = "drop") %>% 
  mutate(value_se = value_sd / sqrt(n),
         lb = value_mean - 1.96 * value_se, 
         ub = value_mean + 1.96 * value_se) %>% 
  mutate(name = sub(".*map\\_", "", name)) %>% 
  mutate(name = factor(name, levels = map_order2)) %>% 
  mutate(type = "high")

xlow %>% 
  bind_rows(xhi) %>% 
  mutate(type = factor(type, levels = c("low", "high"), labels = c("CI < 2", "CI >= 2"))) %>% 
  ggplot(aes(x = name, y = value_mean, color = type)) +
  geom_point(size = 2, position = position_dodge(width = .1)) + 
  geom_errorbar(aes(ymin = lb, ymax = ub), width = .25, linewidth = 1.1, position = position_dodge(width = .1)) +
  scale_color_manual(values = c(col1, col2), name = "Strata") +
  labs(x = "MAP", y = "Minutes", title = "Mean (95% CI) Minutes Spent in Range") +
  scale_y_continuous(breaks = seq(0, 30, 5)) +
  theme(legend.position = "bottom")



```

#### CVP 

```{r cvp heatmap}
mapping %>% 
  select(id, (starts_with("cvp") & !contains("map"))) %>% 
  pivot_longer(cols = -id) %>% 
  group_by(name) %>% 
  summarize(n = n(), 
            across(value, .fns = list(mean = mean, sd = sd)),
            .groups = "drop") %>% 
  mutate(value_se = value_sd / sqrt(n),
         lb = value_mean - 1.96 * value_se, 
         ub = value_mean + 1.96 * value_se) %>% 
  mutate(name = sub(".*cvp\\_", "", name)) %>% 
  mutate(name = factor(name, levels = cvp_order2)) %>% 
  ggplot(aes(x = name, y = value_mean)) +
  geom_point(size = 2) + 
  geom_errorbar(aes(ymin = lb, ymax = ub), width = .25, linewidth = 1.1) +
  # scale_color_viridis() +
  theme(legend.position = "none") +
  labs(x = "CVP", y = "Minutes", title = "Mean (95% CI) Minutes Spent in Range") +
  scale_y_continuous(breaks = seq(0, 30, 5))

xlow = 
  mapping_cilow %>% 
  select(id, (starts_with("cvp") & !contains("map"))) %>% 
  pivot_longer(cols = -id) %>% 
  group_by(name) %>% 
  summarize(n = n(), 
            across(value, .fns = list(mean = mean, sd = sd)),
            .groups = "drop") %>% 
  mutate(value_se = value_sd / sqrt(n),
         lb = value_mean - 1.96 * value_se, 
         ub = value_mean + 1.96 * value_se) %>% 
  mutate(name = sub(".*cvp\\_", "", name)) %>% 
  mutate(name = factor(name, levels = cvp_order2)) %>% 
  mutate(type = "low")

xhi = 
  mapping_cihigh %>% 
  select(id, (starts_with("cvp") & !contains("map"))) %>% 
  pivot_longer(cols = -id) %>% 
  group_by(name) %>% 
  summarize(n = n(), 
            across(value, .fns = list(mean = mean, sd = sd)),
            .groups = "drop") %>% 
  mutate(value_se = value_sd / sqrt(n),
         lb = value_mean - 1.96 * value_se, 
         ub = value_mean + 1.96 * value_se) %>% 
  mutate(name = sub(".*cvp\\_", "", name)) %>% 
  mutate(name = factor(name, levels = cvp_order2)) %>% 
  mutate(type = "high")

xlow %>% 
  bind_rows(xhi) %>% 
  mutate(type = factor(type, levels = c("low", "high"), labels = c("CI < 2", "CI >= 2"))) %>% 
  ggplot(aes(x = name, y = value_mean, color = type)) +
  geom_point(size = 2, position = position_dodge(width = .1)) + 
  geom_errorbar(aes(ymin = lb, ymax = ub), width = .25, linewidth = 1.1, position = position_dodge(width = .1)) +
  scale_color_manual(values = c(col1, col2), name = "Strata") +
  labs(x = "CVP", y = "Minutes", title = "Mean (95% CI) Minutes Spent in Range") +
  scale_y_continuous(breaks = seq(0, 30, 5)) +
  theme(legend.position = "bottom")



```




#### MAP and CVP 


```{r bricks heatmap}
mapping %>% 
  select(id, contains("cvp") & contains("map")) %>% 
  pivot_longer(cols = -id) %>% 
  group_by(name) %>% 
  summarize(n = n(), 
            across(value, .fns = list(mean = mean, sd = sd)),
            .groups = "drop") %>% 
  mutate(value_se = value_sd / sqrt(n),
         lb = value_mean - 1.96 * value_se, 
         ub = value_mean + 1.96 * value_se) %>% 
  separate_wider_delim(cols = name, delim = "_",
                       names = c("x", "map", "x2", "cvp")) %>% 
  mutate(map = factor(map, levels = map_order3),
         cvp = factor(cvp, levels = cvp_order2),
         lab = glue::glue("{round(value_mean)} ({round(value_sd)})")) %>% 
  ggplot(aes(x = map, y = cvp, label = lab)) +
  geom_tile(color = "black", aes(fill = value_mean), alpha = .9) +
  theme(legend.position = "none") +
  scale_fill_paletteer_c("grDevices::YlOrRd", direction = 1) +
  geom_text() +
  labs(x = "MAP", y = "CVP", title = "Mean (SD) Minutes in Range")

xhi = 
  mapping_cihigh %>% 
  select(id, contains("cvp") & contains("map")) %>% 
  pivot_longer(cols = -id) %>% 
  group_by(name) %>% 
  summarize(n = n(), 
            across(value, .fns = list(mean = mean, sd = sd)),
            .groups = "drop") %>% 
  mutate(value_se = value_sd / sqrt(n),
         lb = value_mean - 1.96 * value_se, 
         ub = value_mean + 1.96 * value_se) %>% 
  separate_wider_delim(cols = name, delim = "_",
                       names = c("x", "map", "x2", "cvp")) %>% 
  mutate(map = factor(map, levels = map_order3),
         cvp = factor(cvp, levels = cvp_order2),
         lab = glue::glue("{round(value_mean)} ({round(value_sd)})"),
         type = "high")

xlow = 
  mapping_cilow %>% 
  select(id, contains("cvp") & contains("map")) %>% 
  pivot_longer(cols = -id) %>% 
  group_by(name) %>% 
  summarize(n = n(), 
            across(value, .fns = list(mean = mean, sd = sd)),
            .groups = "drop") %>% 
  mutate(value_se = value_sd / sqrt(n),
         lb = value_mean - 1.96 * value_se, 
         ub = value_mean + 1.96 * value_se) %>% 
  separate_wider_delim(cols = name, delim = "_",
                       names = c("x", "map", "x2", "cvp")) %>% 
  mutate(map = factor(map, levels = map_order3),
         cvp = factor(cvp, levels = cvp_order2),
         lab = glue::glue("{round(value_mean)} ({round(value_sd)})"),
         type = "low")

xhi %>% 
  bind_rows(xlow) %>% 
  mutate(type = factor(type, levels = c("low", "high"), labels = c("CI < 2", "CI >= 2"))) %>% 
  ggplot(aes(x = map, y = cvp, label = lab)) +
  geom_tile(color = "black", aes(fill = value_mean), alpha = .9) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 30)) +
  scale_fill_paletteer_c("grDevices::YlOrRd", direction = 1) +
  geom_text() +
  facet_grid(~type) + 
  labs(x = "MAP", y = "CVP", title = "Mean (SD) Minutes in Range") 


```

```{r bricks heatmap npct}
mapping %>% 
  select(id, contains("cvp") & contains("map")) %>% 
  pivot_longer(cols = -id) %>% 
  group_by(name) %>% 
  summarize(n = n(), 
            across(value, ~sum(.x >= 5)),
            .groups = "drop") %>% 
  mutate(pct = value / n * 100) %>% 
  separate_wider_delim(cols = name, delim = "_",
                       names = c("x", "map", "x2", "cvp")) %>% 
  mutate(map = factor(map, levels = map_order3),
         cvp = factor(cvp, levels = cvp_order2),
         lab = glue::glue("{value} ({round(pct, 0)})")) %>% 
  ggplot(aes(x = map, y = cvp, label = lab)) +
  geom_tile(color = "black", aes(fill = value), alpha = .9) +
  theme(legend.position = "none") +
  scale_fill_paletteer_c("grDevices::YlOrRd", direction = 1) +
  geom_text() +
  labs(x = "MAP", y = "CVP", title = "n (%) Pts with >= 5 Minutes in Range")

xhi = 
  mapping_cihigh %>% 
  select(id, contains("cvp") & contains("map")) %>% 
  pivot_longer(cols = -id) %>% 
  group_by(name) %>% 
  summarize(n = n(), 
            across(value, ~sum(.x >= 5)),
            .groups = "drop") %>% 
  mutate(pct = value / n * 100) %>% 
  separate_wider_delim(cols = name, delim = "_",
                       names = c("x", "map", "x2", "cvp")) %>% 
  mutate(map = factor(map, levels = map_order3),
         cvp = factor(cvp, levels = cvp_order2),
         lab = glue::glue("{value} ({round(pct, 0)})"),
         type = "high")
xlow = 
  mapping_cilow %>% 
  select(id, contains("cvp") & contains("map")) %>% 
  pivot_longer(cols = -id) %>% 
  group_by(name) %>% 
  summarize(n = n(), 
            across(value, ~sum(.x >= 5)),
            .groups = "drop") %>% 
  mutate(pct = value / n * 100) %>% 
  separate_wider_delim(cols = name, delim = "_",
                       names = c("x", "map", "x2", "cvp")) %>% 
  mutate(map = factor(map, levels = map_order3),
         cvp = factor(cvp, levels = cvp_order2),
         lab = glue::glue("{value} ({round(pct, 0)})"),
         type = "low")

xhi %>% 
  bind_rows(xlow) %>% 
  mutate(type = factor(type, levels = c("low", "high"), labels = c("CI < 2", "CI >= 2"))) %>% 
  ggplot(aes(x = map, y = cvp, label = lab)) +
  geom_tile(color = "black", aes(fill = value), alpha = .9) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 30)) +
  scale_fill_paletteer_c("grDevices::YlOrRd", direction = 1) +
  geom_text(size = 2.5) +
  facet_grid(~type) + 
  labs(x = "MAP", y = "CVP", title = "n (%) Pts with >= 5 Minutes in Range",
       subtitle = "Stratified by CI")



xhi = 
  mapping_cihigh %>% 
  select(id, contains("cvp") & contains("map")) %>% 
  pivot_longer(cols = -id) %>% 
  mutate(aki = if_else(id %in% aki_ids, "AKI: Yes", "AKI: No")) %>% 
  group_by(name, aki) %>% 
  summarize(n = n(), 
            across(value, ~sum(.x >= 5)),
            .groups = "drop") %>% 
  mutate(pct = value / n * 100) %>% 
  separate_wider_delim(cols = name, delim = "_",
                       names = c("x", "map", "x2", "cvp")) %>% 
  mutate(map = factor(map, levels = map_order3),
         cvp = factor(cvp, levels = cvp_order2),
         lab = glue::glue("{value} ({round(pct, 0)})"),
         type = "high")
xlow = 
  mapping_cilow %>% 
  select(id, contains("cvp") & contains("map")) %>% 
  pivot_longer(cols = -id) %>% 
  mutate(aki = if_else(id %in% aki_ids, "AKI: Yes", "AKI: No")) %>% 
  group_by(name, aki) %>% 
  summarize(n = n(), 
            across(value, ~sum(.x >= 5)),
            .groups = "drop") %>% 
  mutate(pct = value / n * 100) %>% 
  separate_wider_delim(cols = name, delim = "_",
                       names = c("x", "map", "x2", "cvp")) %>% 
  mutate(map = factor(map, levels = map_order3),
         cvp = factor(cvp, levels = cvp_order2),
         lab = glue::glue("{value} ({round(pct, 0)})"),
         type = "low")

xhi %>% 
  bind_rows(xlow) %>% 
  mutate(type = factor(type, levels = c("low", "high"), labels = c("CI < 2", "CI >= 2"))) %>% 
  ggplot(aes(x = map, y = cvp, label = lab)) +
  geom_tile(color = "black", aes(fill = pct), alpha = .9) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 30)) +
  scale_fill_paletteer_c("grDevices::YlOrRd", direction = 1) +
  geom_text(size = 2) +
  facet_grid(aki~type) + 
  labs(x = "MAP", y = "CVP", title = "n (%) Pts with >= 5 Minutes in Range",
       subtitle = "Stratified by CI and AKI")


```

#### Zones (5)

```{r zones 5 table}
mapping %>%  
  mutate(across(everything(), ~replace_na(.x, 0))) %>% 
  select(id, contains("shell")) %>% 
  rename_with(.cols = starts_with("shell"), ~sub("shell", "zone", .x)) %>% 
  tbl_summary(
    include = -id,
    statistic = all_continuous() ~ "{mean} ({sd})") %>% 
   modify_caption("Minutes in Zone") 

mapping_cihigh %>%  
  mutate(across(everything(), ~replace_na(.x, 0))) %>% 
  select(id, contains("shell")) %>% 
  mutate(type = "CI >= 2") %>% 
  bind_rows(mapping_cilow %>%  
  mutate(across(everything(), ~replace_na(.x, 0))) %>% 
  select(id, contains("shell")) %>% 
  mutate(type = "CI < 2")) %>% 
  rename_with(.cols = starts_with("shell"), ~sub("shell", "zone", .x)) %>% 
  tbl_summary(
    include = -id,
    by = type,
    statistic = all_continuous() ~ "{mean} ({sd})") %>% 
  modify_caption("Minutes in Zone, Stratified by CI") 
```

```{r zones 5 table n pct}
mapping %>%  
  mutate(across(everything(), ~replace_na(.x, 0))) %>% 
  select(id, contains("shell")) %>% 
  rename_with(.cols = starts_with("shell"), ~sub("shell", "zone", .x)) %>%
  pivot_longer(cols = -id) %>% 
  group_by(name) %>%   
  summarize(n = n(),
            value = sum(value >= 5),
            .groups = "drop") %>% 
  mutate(pct = value / n * 100) %>% 
  select(-n) %>% 
  gt() %>% 
  fmt_number(columns = pct, decimals = 0) %>% 
  cols_label(name = "Zone",
             value = "n >= 5 min",
             pct = "% >= 5 min") %>% 
  data_color(
    columns = value,
    target_columns = c(value, pct),
    palette = "YlOrRd"
  ) %>% 
  tab_header(title = "n (%) with at least 5 minutes in Zone")
  
thigh = 
  mapping_cihigh %>%  
  mutate(across(everything(), ~replace_na(.x, 0))) %>% 
  select(id, contains("shell")) %>% 
  rename_with(.cols = starts_with("shell"), ~sub("shell", "zone", .x)) %>%
  pivot_longer(cols = -id) %>% 
  group_by(name) %>%   
  summarize(n = n(),
            value = sum(value >= 5),
            .groups = "drop") %>% 
  mutate(pct = value / n * 100) %>% 
  select(-n) 

tlow =
  mapping_cilow %>%  
  mutate(across(everything(), ~replace_na(.x, 0))) %>% 
  select(id, contains("shell")) %>% 
  rename_with(.cols = starts_with("shell"), ~sub("shell", "zone", .x)) %>%
  pivot_longer(cols = -id) %>% 
  group_by(name) %>%   
  summarize(n = n(),
            value = sum(value >= 5),
            .groups = "drop") %>% 
  mutate(pct = value / n * 100) %>% 
  select(-n) 

tlow %>% 
  mutate(type = "CI < 2") %>% 
  bind_rows(thigh %>%  
  mutate(type = "CI >= 2")) %>% 
  group_by(type) %>% 
  gt() %>% 
  fmt_number(columns = pct, decimals = 0) %>% 
  cols_label(name = "Zone",
             value = "n >= 5 min",
             pct = "% >= 5 min") %>% 
  data_color(
    columns = pct,
    target_columns = c(value, pct),
    palette = "YlOrRd"
  ) %>% 
  tab_header(title = "n (%) with at least 5 minutes in Zone",
             subtitle = "Strafied by CI")
  
```

```{r zones 5 table n pct, aki}
mapping %>%  
  mutate(across(everything(), ~replace_na(.x, 0))) %>% 
  select(id, contains("shell")) %>% 
  mutate(aki = if_else(id %in% aki_ids, "AKI: Yes", "AKI: No")) %>% 
  rename_with(.cols = starts_with("shell"), ~sub("shell", "zone", .x)) %>%
  pivot_longer(cols = -c(id, aki)) %>% 
  group_by(name, aki) %>%   
  summarize(n = n(),
            value = sum(value >= 5),
            .groups = "drop") %>% 
  mutate(pct = value / n * 100) %>% 
  select(-n) %>% 
  group_by(aki) %>% 
  gt() %>% 
  fmt_number(columns = pct, decimals = 0) %>% 
  cols_label(name = "Zone",
             value = "n >= 5 min",
             pct = "% >= 5 min") %>% 
  data_color(
    columns = pct,
    target_columns = c(value, pct),
    palette = "YlOrRd"
  ) %>% 
  tab_header(title = "n (%) with at least 5 minutes in Zone",
             subtitle = "Stratified by AKI") 
  
thigh = 
  mapping_cihigh %>%  
  mutate(aki = if_else(id %in% aki_ids, "AKI: Yes", "AKI: No")) %>% 
  mutate(across(everything(), ~replace_na(.x, 0))) %>% 
  select(id, aki, contains("shell")) %>% 
  rename_with(.cols = starts_with("shell"), ~sub("shell", "zone", .x)) %>%
  pivot_longer(cols = -c(aki, id)) %>% 
  group_by(name, aki) %>%   
  summarize(n = n(),
            value = sum(value >= 5),
            .groups = "drop") %>% 
  mutate(pct = value / n * 100) %>% 
  select(-n) 

tlow =
  mapping_cilow %>%  
  mutate(aki = if_else(id %in% aki_ids, "AKI: Yes", "AKI: No")) %>% 
  mutate(across(everything(), ~replace_na(.x, 0))) %>% 
  select(id, aki, contains("shell")) %>% 
  rename_with(.cols = starts_with("shell"), ~sub("shell", "zone", .x)) %>%
  pivot_longer(cols = -c(aki, id)) %>% 
  group_by(name, aki) %>% 
  summarize(n = n(),
            value = sum(value >= 5),
            .groups = "drop") %>% 
  mutate(pct = value / n * 100) %>% 
  select(-n) 

tlow %>% 
  mutate(type = "CI < 2") %>% 
  bind_rows(thigh %>%  
  mutate(type = "CI >= 2")) %>% 
  group_by(type, aki) %>% 
  gt() %>% 
  fmt_number(columns = pct, decimals = 0) %>% 
  cols_label(name = "Zone",
             value = "n >= 5 min",
             pct = "% >= 5 min") %>% 
  data_color(
    columns = pct,
    target_columns = c(value, pct),
    palette = "YlOrRd"
  ) %>% 
  tab_header(title = "n (%) with at least 5 minutes in Zone",
             subtitle = "Strafied by CI and AKI")
  
```

#### Zones (3)


```{r zones 3 table}
mapping %>%  
  mutate(across(everything(), ~replace_na(.x, 0))) %>% 
  select(id, contains("zone")) %>% 
  tbl_summary(
    include = -id,
    statistic = all_continuous() ~ "{mean} ({sd})") %>% 
   modify_caption("Minutes in Zone") 

mapping_cihigh %>%  
  mutate(across(everything(), ~replace_na(.x, 0))) %>% 
  select(id, contains("zone")) %>% 
  mutate(type = "CI >= 2") %>% 
  bind_rows(mapping_cilow %>%  
  mutate(across(everything(), ~replace_na(.x, 0))) %>% 
  select(id, contains("zone")) %>% 
  mutate(type = "CI < 2")) %>% 
  tbl_summary(
    include = -id,
    by = type,
    statistic = all_continuous() ~ "{mean} ({sd})") %>% 
  modify_caption("Minutes in Zone, Stratified by CI") 
```

```{r zones 3 table n pct}
mapping %>%  
  mutate(across(everything(), ~replace_na(.x, 0))) %>% 
  select(id, contains("zone")) %>% 
  pivot_longer(cols = -id) %>% 
  group_by(name) %>%   
  summarize(n = n(),
            value = sum(value >= 5),
            .groups = "drop") %>% 
  mutate(pct = value / n * 100) %>% 
  select(-n) %>% 
  gt() %>% 
  fmt_number(columns = pct, decimals = 0) %>% 
  cols_label(name = "Zone",
             value = "n >= 5 min",
             pct = "% >= 5 min") %>% 
  data_color(
    columns = value,
    target_columns = c(value, pct),
    palette = "YlOrRd"
  ) %>% 
  tab_header(title = "n (%) with at least 5 minutes in Zone")
  
thigh = 
  mapping_cihigh %>%  
  mutate(across(everything(), ~replace_na(.x, 0))) %>% 
  select(id, contains("zone")) %>% 
  pivot_longer(cols = -id) %>% 
  group_by(name) %>%   
  summarize(n = n(),
            value = sum(value >= 5),
            .groups = "drop") %>% 
  mutate(pct = value / n * 100) %>% 
  select(-n) 

tlow =
  mapping_cilow %>%  
  mutate(across(everything(), ~replace_na(.x, 0))) %>% 
  select(id, contains("zone")) %>% 
  pivot_longer(cols = -id) %>% 
  group_by(name) %>%   
  summarize(n = n(),
            value = sum(value >= 5),
            .groups = "drop") %>% 
  mutate(pct = value / n * 100) %>% 
  select(-n) 

tlow %>% 
  mutate(type = "CI < 2") %>% 
  bind_rows(thigh %>%  
  mutate(type = "CI >= 2")) %>% 
  group_by(type) %>% 
  gt() %>% 
  fmt_number(columns = pct, decimals = 0) %>% 
  cols_label(name = "Zone",
             value = "n >= 5 min",
             pct = "% >= 5 min") %>% 
  data_color(
    columns = pct,
    target_columns = c(value, pct),
    palette = "YlOrRd"
  ) %>% 
  tab_header(title = "n (%) with at least 5 minutes in Zone",
             subtitle = "Strafied by CI")
  
```

```{r zones 3 table n pct, aki}
mapping %>%  
  mutate(across(everything(), ~replace_na(.x, 0))) %>% 
  select(id, contains("zone")) %>% 
  mutate(aki = if_else(id %in% aki_ids, "AKI: Yes", "AKI: No")) %>% 
  pivot_longer(cols = -c(id, aki)) %>% 
  group_by(name, aki) %>%   
  summarize(n = n(),
            value = sum(value >= 5),
            .groups = "drop") %>% 
  mutate(pct = value / n * 100) %>% 
  select(-n) %>% 
  group_by(aki) %>% 
  gt() %>% 
  fmt_number(columns = pct, decimals = 0) %>% 
  cols_label(name = "Zone",
             value = "n >= 5 min",
             pct = "% >= 5 min") %>% 
  data_color(
    columns = pct,
    target_columns = c(value, pct),
    palette = "YlOrRd"
  ) %>% 
  tab_header(title = "n (%) with at least 5 minutes in Zone",
             subtitle = "Stratified by AKI") 
  
thigh = 
  mapping_cihigh %>%  
  mutate(aki = if_else(id %in% aki_ids, "AKI: Yes", "AKI: No")) %>% 
  mutate(across(everything(), ~replace_na(.x, 0))) %>% 
  select(id, aki, contains("zone")) %>% 
  pivot_longer(cols = -c(aki, id)) %>% 
  group_by(name, aki) %>%   
  summarize(n = n(),
            value = sum(value >= 5),
            .groups = "drop") %>% 
  mutate(pct = value / n * 100) %>% 
  select(-n) 

tlow =
  mapping_cilow %>%  
  mutate(aki = if_else(id %in% aki_ids, "AKI: Yes", "AKI: No")) %>% 
  mutate(across(everything(), ~replace_na(.x, 0))) %>% 
  select(id, aki, contains("zone")) %>% 
  pivot_longer(cols = -c(aki, id)) %>% 
  group_by(name, aki) %>% 
  summarize(n = n(),
            value = sum(value >= 5),
            .groups = "drop") %>% 
  mutate(pct = value / n * 100) %>% 
  select(-n) 

tlow %>% 
  mutate(type = "CI < 2") %>% 
  bind_rows(thigh %>%  
  mutate(type = "CI >= 2")) %>% 
  group_by(type, aki) %>% 
  gt() %>% 
  fmt_number(columns = pct, decimals = 0) %>% 
  cols_label(name = "Zone",
             value = "n >= 5 min",
             pct = "% >= 5 min") %>% 
  data_color(
    columns = pct,
    target_columns = c(value, pct),
    palette = "YlOrRd"
  ) %>% 
  tab_header(title = "n (%) with at least 5 minutes in Zone",
             subtitle = "Strafied by CI and AKI")
  
```


#### Physiological Zones

```{r pzones heatmap}
pzones %>% 
  pivot_longer(cols = -id) %>% 
  group_by(name) %>% 
  summarize(n = n(), 
            across(value, .fns = list(mean = mean, sd = sd)),
            .groups = "drop") %>% 
  mutate(value_se = value_sd / sqrt(n),
         lb = value_mean - 1.96 * value_se, 
         ub = value_mean + 1.96 * value_se) %>% 
  separate_wider_delim(cols = name, delim = "_",
                       names = c("x", "map", "x2", "cvp")) %>% 
  mutate(lab = glue::glue("{round(value_mean)} ({round(value_sd)})")) %>% 
  ggplot(aes(x = map, y = cvp, label = lab)) +
  geom_tile(color = "black", aes(fill = value_mean), alpha = .9) +
  theme(legend.position = "none") +
  scale_fill_paletteer_c("grDevices::YlOrRd", direction = 1) +
  geom_text() +
  labs(x = "MAP", y = "CVP", title = "Mean (SD) Minutes in Range")

xhi = 
  pzones_hi %>% 
  pivot_longer(cols = -id) %>% 
  group_by(name) %>% 
  summarize(n = n(), 
            across(value, .fns = list(mean = mean, sd = sd)),
            .groups = "drop") %>% 
  mutate(value_se = value_sd / sqrt(n),
         lb = value_mean - 1.96 * value_se, 
         ub = value_mean + 1.96 * value_se) %>% 
  separate_wider_delim(cols = name, delim = "_",
                       names = c("x", "map", "x2", "cvp")) %>% 
  mutate(lab = glue::glue("{round(value_mean)} ({round(value_sd)})"),
         type = "high")

xlow = 
  pzones_low %>% 
  pivot_longer(cols = -id) %>% 
  group_by(name) %>% 
  summarize(n = n(), 
            across(value, .fns = list(mean = mean, sd = sd)),
            .groups = "drop") %>% 
  mutate(value_se = value_sd / sqrt(n),
         lb = value_mean - 1.96 * value_se, 
         ub = value_mean + 1.96 * value_se) %>% 
  separate_wider_delim(cols = name, delim = "_",
                       names = c("x", "map", "x2", "cvp")) %>% 
  mutate(lab = glue::glue("{round(value_mean)} ({round(value_sd)})"),
         type = "low")

xhi %>% 
  bind_rows(xlow) %>% 
  mutate(type = factor(type, levels = c("low", "high"), labels = c("CI < 2", "CI >= 2"))) %>% 
  ggplot(aes(x = map, y = cvp, label = lab)) +
  geom_tile(color = "black", aes(fill = value_mean), alpha = .9) +
  theme(legend.position = "none") +
  scale_fill_paletteer_c("grDevices::YlOrRd", direction = 1) +
  geom_text() +
  facet_grid(~type) + 
  labs(x = "MAP", y = "CVP", title = "Mean (SD) Minutes in Range") 


```

```{r pzones heatmap npct}
pzones %>% 
  pivot_longer(cols = -id) %>% 
  group_by(name) %>% 
  summarize(n = n(), 
            across(value, ~sum(.x >= 5)),
            .groups = "drop") %>% 
  mutate(pct = value / n * 100) %>% 
  separate_wider_delim(cols = name, delim = "_",
                       names = c("x", "map", "x2", "cvp")) %>% 
  mutate(lab = glue::glue("{value} ({round(pct, 0)})")) %>% 
  ggplot(aes(x = map, y = cvp, label = lab)) +
  geom_tile(color = "black", aes(fill = value), alpha = .9) +
  theme(legend.position = "none") +
  scale_fill_paletteer_c("grDevices::YlOrRd", direction = 1) +
  geom_text() +
  labs(x = "MAP", y = "CVP", title = "n (%) Pts with >= 5 Minutes in Range")

xhi = 
  pzones_hi %>% 
  pivot_longer(cols = -id) %>% 
  group_by(name) %>% 
  summarize(n = n(), 
            across(value, ~sum(.x >= 5)),
            .groups = "drop") %>% 
  mutate(pct = value / n * 100) %>% 
  separate_wider_delim(cols = name, delim = "_",
                       names = c("x", "map", "x2", "cvp")) %>% 
  mutate(lab = glue::glue("{value} ({round(pct, 0)})"),
         type = "high")
xlow = 
  pzones_low %>% 
  pivot_longer(cols = -id) %>% 
  group_by(name) %>% 
  summarize(n = n(), 
            across(value, ~sum(.x >= 5)),
            .groups = "drop") %>% 
  mutate(pct = value / n * 100) %>% 
  separate_wider_delim(cols = name, delim = "_",
                       names = c("x", "map", "x2", "cvp")) %>% 
  mutate(lab = glue::glue("{value} ({round(pct, 0)})"),
         type = "low")

xhi %>% 
  bind_rows(xlow) %>% 
  mutate(type = factor(type, levels = c("low", "high"), labels = c("CI < 2", "CI >= 2"))) %>% 
  ggplot(aes(x = map, y = cvp, label = lab)) +
  geom_tile(color = "black", aes(fill = value), alpha = .9) +
  theme(legend.position = "none") +
  scale_fill_paletteer_c("grDevices::YlOrRd", direction = 1) +
  geom_text() +
  facet_grid(~type) + 
  labs(x = "MAP", y = "CVP", title = "n (%) Pts with >= 5 Minutes in Range",
       subtitle = "Stratified by CI")



xhi = 
  pzones_hi %>% 
  pivot_longer(cols = -id) %>% 
  mutate(aki = if_else(id %in% aki_ids, "AKI: Yes", "AKI: No")) %>% 
  group_by(name, aki) %>% 
  summarize(n = n(), 
            across(value, ~sum(.x >= 5)),
            .groups = "drop") %>% 
  mutate(pct = value / n * 100) %>% 
  separate_wider_delim(cols = name, delim = "_",
                       names = c("x", "map", "x2", "cvp")) %>% 
  mutate(lab = glue::glue("{value} ({round(pct, 0)})"),
         type = "high")
xlow = 
  pzones_low %>% 
  pivot_longer(cols = -id) %>% 
  mutate(aki = if_else(id %in% aki_ids, "AKI: Yes", "AKI: No")) %>% 
  group_by(name, aki) %>% 
  summarize(n = n(), 
            across(value, ~sum(.x >= 5)),
            .groups = "drop") %>% 
  mutate(pct = value / n * 100) %>% 
  separate_wider_delim(cols = name, delim = "_",
                       names = c("x", "map", "x2", "cvp")) %>% 
  mutate(lab = glue::glue("{value} ({round(pct, 0)})"),
         type = "low")

xhi %>% 
  bind_rows(xlow) %>% 
  mutate(type = factor(type, levels = c("low", "high"), labels = c("CI < 2", "CI >= 2"))) %>% 
  ggplot(aes(x = map, y = cvp, label = lab)) +
  geom_tile(color = "black", aes(fill = pct), alpha = .9) +
  theme(legend.position = "none") +
  scale_fill_paletteer_c("grDevices::YlOrRd", direction = 1) +
  geom_text() +
  facet_grid(aki~type) + 
  labs(x = "MAP", y = "CVP", title = "n (%) Pts with >= 5 Minutes in Range",
       subtitle = "Stratified by CI and AKI")


```

### Fine Mapping Analysis {.tabset}

Variables that we will control for are: `r covars_control`

In this section, we are just modeling one zone at a time, with or without covariates.

Significance label key

| p-value | label |
|---------|-------|
| <0.001  | ***   |
| <.01    | **    |
| <.05    | *     |
| <.1     | .     |
| >=0.1   |       |

#### MAP

```{r map j plot}
temp_df = 
  mapping %>% 
  select(id, (starts_with("map") & !contains("cvp")))
  
res_mult = run_regression(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control, hemo_type = "map")

res_uni = run_regression(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control, hemo_type = "map", adjustment_type = "uni")

res_mult %>% 
  mutate(model = "adjusted") %>% 
  bind_rows(res_uni %>% mutate(model = "unadjusted")) %>% 
  mutate(model = factor(model, levels = c("unadjusted", "adjusted"))) %>% 
  mutate(term = sub(".*`map\\_(.+)`.*", "\\1", term),
         term = factor(term, levels = map_order2)) %>% 
  ggplot(aes(x = term, y = estimate, color = model)) +
  geom_point(position = position_dodge(width = .25)) +
  geom_errorbar(position = position_dodge(width = .25),
                aes(ymin = lb, ymax = ub), width = .25) +
  scale_color_manual(values = c(col1a, col2a), name = "Model") +
  geom_hline(aes(yintercept = 1), color = "darkgrey") +
  scale_y_continuous(breaks = seq(.4, 1.6, .2)) +
  theme(legend.position = "bottom") +
  labs(x = "MAP", y = "Odds Ratio per 5 min in Range",
       title = "MAP Ranges and AKI")

## low CI
temp_df = 
  mapping_cilow %>% 
  select(id, (starts_with("map") & !contains("cvp")))
  
res_mult = run_regression(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control, hemo_type = "map")

res_uni = run_regression(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control, hemo_type = "map", adjustment_type = "uni")

res_mult_low = 
  res_mult %>% 
  mutate(model = "adjusted") %>% 
  bind_rows(res_uni %>% mutate(model = "unadjusted")) %>% 
  mutate(type = "CI < 2")

temp_df = 
  mapping_cihigh %>% 
  select(id, (starts_with("map") & !contains("cvp")))
  
res_mult = run_regression(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control, hemo_type = "map")

res_uni = run_regression(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control, hemo_type = "map", adjustment_type = "uni")

res_mult_high = 
  res_mult %>% 
  mutate(model = "adjusted") %>% 
  bind_rows(res_uni %>% mutate(model = "unadjusted")) %>% 
  mutate(type = "CI >= 2")
  
res_mult_low %>% 
  bind_rows(res_mult_high) %>% 
  mutate(model = factor(model, levels = c("unadjusted", "adjusted"))) %>% 
  mutate(term = sub(".*`map\\_(.+)`.*", "\\1", term),
         term = factor(term, levels = map_order2)) %>% 
  ggplot(aes(x = term, y = estimate, color = model)) +
  geom_point(position = position_dodge(width = .25)) +
  geom_errorbar(position = position_dodge(width = .25),
                aes(ymin = lb, ymax = ub), width = .25) +
  scale_color_manual(values = c(col1a, col2a), name = "Model") +
  geom_hline(aes(yintercept = 1), color = "darkgrey") +
  theme(legend.position = "bottom") +
  labs(x = "MAP", y = "Odds Ratio per 5 min in Range",
       title = "MAP Ranges and AKI, Stratified by CI") +
  facet_grid(type ~ .)
 
```

#### CVP

```{r cvp j plot}
temp_df = 
  mapping %>% 
  select(id, (starts_with("cvp") & !contains("map")))
  
res_mult = run_regression(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control, hemo_type = "cvp")

res_uni = run_regression(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control, hemo_type = "cvp", adjustment_type = "uni")

res_mult %>% 
  mutate(model = "adjusted") %>% 
  bind_rows(res_uni %>% mutate(model = "unadjusted")) %>% 
  mutate(model = factor(model, levels = c("unadjusted", "adjusted"))) %>% 
  mutate(term = sub(".*`cvp\\_(.+)`.*", "\\1", term),
         term = factor(term, levels = cvp_order2)) %>% 
  ggplot(aes(x = term, y = estimate, color = model)) +
  geom_point(position = position_dodge(width = .25)) +
  geom_errorbar(position = position_dodge(width = .25),
                aes(ymin = lb, ymax = ub), width = .25) +
  scale_color_manual(values = c(col1a, col2a), name = "Model") +
  geom_hline(aes(yintercept = 1), color = "darkgrey") +
  scale_y_continuous(breaks = seq(.8, 1.6, .05)) +
  theme(legend.position = "bottom") +
  labs(x = "CVP", y = "Odds Ratio per 5 min in Range",
       title = "CVP Ranges and AKI")

## low CI
temp_df = 
  mapping_cilow %>% 
  select(id, (starts_with("cvp") & !contains("map")))
  
res_mult = run_regression(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control, hemo_type = "cvp")

res_uni = run_regression(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control, hemo_type = "cvp", adjustment_type = "uni")

res_mult_low = 
  res_mult %>% 
  mutate(model = "adjusted") %>% 
  bind_rows(res_uni %>% mutate(model = "unadjusted")) %>% 
  mutate(type = "CI < 2")

temp_df = 
  mapping_cihigh %>% 
  select(id, (starts_with("cvp") & !contains("map")))
  
res_mult = run_regression(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control, hemo_type = "cvp")

res_uni = run_regression(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control, hemo_type = "cvp", adjustment_type = "uni")

res_mult_high = 
  res_mult %>% 
  mutate(model = "adjusted") %>% 
  bind_rows(res_uni %>% mutate(model = "unadjusted")) %>% 
  mutate(type = "CI >= 2")
  
res_mult_low %>% 
  bind_rows(res_mult_high) %>% 
  mutate(model = factor(model, levels = c("unadjusted", "adjusted"))) %>% 
  mutate(term = sub(".*`cvp\\_(.+)`.*", "\\1", term),
         term = factor(term, levels = cvp_order2)) %>% 
  ggplot(aes(x = term, y = estimate, color = model)) +
  geom_point(position = position_dodge(width = .25)) +
  geom_errorbar(position = position_dodge(width = .25),
                aes(ymin = lb, ymax = ub), width = .25) +
  scale_color_manual(values = c(col1a, col2a), name = "Model") +
  geom_hline(aes(yintercept = 1), color = "darkgrey") +
  theme(legend.position = "bottom") +
  labs(x = "CVP", y = "Odds Ratio per 5 min in Range",
       title = "CVP Ranges and AKI, Stratified by CI") +
  facet_grid(type ~ .)
 
```


#### MAP and CVP


```{r bivar zones}
temp_df = 
  mapping %>% 
  select(id, contains("cvp") & contains("map"))
  
res_mult = run_regression_biv(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control)

res_uni = run_regression_biv(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control, adjustment_type = "uni")

res_uni %>% 
  separate_wider_delim(term, delim = "_",
                       names = c("x", "map", "x2", "cvp")) %>% 
  mutate(cvp = sub("`.*", "", cvp)) %>% 
  mutate(map = factor(map, levels = map_order3),
         cvp = factor(cvp, levels = cvp_order2),
         sig = case_when(p.value < .01 ~ "***",
                         p.value < .01 ~ "**",
                         p.value < .05 ~ "*", 
                         p.value < .1 ~ ".",
                         .default = ""),
         lab = glue::glue("{sprintf('%.2f', estimate)} {sig}")) %>% 
  ggplot(aes(x = map, y = cvp, fill = estimate, label = lab)) +
  geom_tile(color = "black") +
  geom_text() +
  labs(x = "MAP", y = "CVP", title = "Fine Mapping, Unadjusted Models",
       subtitle = "OR Associated with 5 min Increase in Time in Range") +
  scale_fill_gradient2(low = "darkblue", mid = "white", high = "red", midpoint = 1, name = "Odds Ratio (OR)") +
  theme(legend.position = "none")

res_mult %>% 
  separate_wider_delim(term, delim = "_",
                       names = c("x", "map", "x2", "cvp")) %>% 
  mutate(cvp = sub("`.*", "", cvp)) %>% 
  mutate(map = factor(map, levels = map_order3),
         cvp = factor(cvp, levels = cvp_order2),
         sig = case_when(p.value < .01 ~ "***",
                         p.value < .01 ~ "**",
                         p.value < .05 ~ "*", 
                         p.value < .1 ~ ".",
                         .default = ""),
         lab = glue::glue("{sprintf('%.2f', estimate)} {sig}")) %>% 
  ggplot(aes(x = map, y = cvp, fill = estimate, label = lab)) +
  geom_tile(color = "black") +
  geom_text() +
  labs(x = "MAP", y = "CVP", title = "Fine Mapping, Adjusted Models",
       subtitle = "OR Associated with 5 min Increase in Time in Range") +
  scale_fill_gradient2(low = "darkblue", mid = "white", high = "red", midpoint = 1, name = "Odds Ratio (OR)") +
  theme(legend.position = "none") 

```


```{r bivar strat zones uni}
# uniivariate 
temp_df = 
  mapping_cihigh %>% 
  select(id, contains("cvp") & contains("map"))
  
res_mult_hi = run_regression_biv(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control,
               adjustment_type = "uni") %>% 
  mutate(type = "CI >= 2")

temp_df = 
  mapping_cilow %>% 
  select(id, contains("cvp") & contains("map"))
  
res_mult_lo = run_regression_biv(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control,
               adjustment_type = "uni") %>% 
  mutate(type = "CI < 2")

res_mult_hi %>% 
  bind_rows(res_mult_lo) %>% 
  separate_wider_delim(term, delim = "_",
                       names = c("x", "map", "x2", "cvp")) %>% 
  mutate(cvp = sub("`.*", "", cvp),
         estimate = if_else(estimate > 10, NA, estimate),
         map = factor(map, levels = map_order3),
         cvp = factor(cvp, levels = cvp_order2),
         sig = case_when(p.value < .01 ~ "***",
                         p.value < .01 ~ "**",
                         p.value < .05 ~ "*", 
                         p.value < .1 ~ ".",
                         .default = ""),
         lab = glue::glue("{sprintf('%.2f', estimate)} {sig}")) %>% 
  ggplot(aes(x = map, y = cvp, fill = estimate, label = lab)) +
  geom_tile(color = "black") +
  geom_text() +
  labs(x = "MAP", y = "CVP", title = "Fine Mapping, Unadjusted Models, Stratified",
       subtitle = "OR Associated with 5 min Increase in Time in Range") +
  scale_fill_gradient2(low = "darkblue", mid = "white", high = "red", midpoint = 1, name = "Odds Ratio (OR)") +
  theme(legend.position = "none") +
  facet_grid(type ~ .)
```



```{r bivar strat zones multi}
# multivariate 
temp_df = 
  mapping_cihigh %>% 
  select(id, contains("cvp") & contains("map"))
  
res_uni_hi = run_regression_biv(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control) %>% 
  mutate(type = "CI >= 2")

temp_df = 
  mapping_cilow %>% 
  select(id, contains("cvp") & contains("map"))
  
res_uni_lo = run_regression_biv(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control) %>% 
  mutate(type = "CI < 2")

res_uni_hi %>% 
  bind_rows(res_uni_lo) %>% 
  separate_wider_delim(term, delim = "_",
                       names = c("x", "map", "x2", "cvp")) %>% 
  mutate(cvp = sub("`.*", "", cvp),
         estimate = if_else(estimate > 10, NA, estimate),
         map = factor(map, levels = map_order3),
         cvp = factor(cvp, levels = cvp_order2),
         sig = case_when(p.value < .01 ~ "***",
                         p.value < .01 ~ "**",
                         p.value < .05 ~ "*", 
                         p.value < .1 ~ ".",
                         .default = ""),
         lab = glue::glue("{sprintf('%.2f', estimate)} {sig}")) %>% 
  ggplot(aes(x = map, y = cvp, fill = estimate, label = lab)) +
  geom_tile(color = "black") +
  geom_text() +
  labs(x = "MAP", y = "CVP", title = "Fine Mapping, Adjusted Models, Stratified",
       subtitle = "OR Associated with 5 min Increase in Time in Range") +
  scale_fill_gradient2(low = "darkblue", mid = "white", high = "red", midpoint = 1, name = "Odds Ratio (OR)") +
  theme(legend.position = "none") +
  facet_grid(type ~ .)
```



#### Zones (5)

```{r zones regression}
temp_df = 
  mapping %>% 
  select(id, contains("shell")) %>% 
  rename_with(.cols = -id, ~sub("shell", "zone", .x))
  
res_mult = run_regression(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control,
               hemo_type = "zone")

res_uni = run_regression(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               hemo_type = "zone", adjustment_type = "uni")

res_uni %>% 
  mutate(type = "unadjusted") %>% 
  bind_rows(res_mult %>% mutate(type = "adjusted")) %>% 
  mutate(est = glue::glue("{sprintf('%.2f', estimate)} ({sprintf('%.2f', lb)}, {sprintf('%.2f', ub)})"),
         sig = case_when(p.value < .01 ~ "***",
                         p.value < .01 ~ "**",
                         p.value < .05 ~ "*", 
                         p.value < .1 ~ ".",
                         .default = "")) %>% 
  select(term, type, est, estimate, sig) %>% 
  group_by(type) %>% 
  # pivot_wider(names_from = type, values_from = c(est, estimate)) %>% 
  gt::gt() %>% 
  data_color(
    columns = estimate,
    target_columns = everything(),
    fn = scales::div_gradient_pal(
      low = "darkblue", 
      mid = "white", 
      high = "red"
    ) %>% 
      {function(x) .(scales::rescale_mid(x, mid = 1))}
  ) %>% 
  cols_hide(columns = estimate) %>% 
  cols_label(term = "Zone",
             est = "OR (95% CI)",
             sig = "Significance") %>% 
  tab_header(title = "Zone Regressions",
             subtitle = "OR per 5 min in Zone")
```

```{r zones strat and unadj}
## stratified and unadjusted

temp_df_lo = 
  mapping_cilow %>% 
  select(id, contains("shell")) %>% 
  rename_with(.cols = -id, ~sub("shell", "zone", .x))
  
temp_df_hi = 
  mapping_cihigh %>% 
  select(id, contains("shell")) %>% 
  rename_with(.cols = -id, ~sub("shell", "zone", .x))

res_hi = run_regression(temp_df_hi, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control,
               hemo_type = "zone",
               adjustment_type = "uni")

res_lo = run_regression(temp_df_lo, 
               covariate_df = df, outcome = "bin_aki48h",
               hemo_type = "zone", adjustment_type = "uni")

res_lo %>% 
  mutate(type = "CI < 2") %>% 
  bind_rows(res_hi %>% mutate(type = "CI >= 2")) %>% 
  mutate(est = glue::glue("{sprintf('%.2f', estimate)} ({sprintf('%.2f', lb)}, {sprintf('%.2f', ub)})"),
         sig = case_when(p.value < .01 ~ "***",
                         p.value < .01 ~ "**",
                         p.value < .05 ~ "*", 
                         p.value < .1 ~ ".",
                         .default = "")) %>% 
  select(term, type, est, estimate, sig) %>% 
  group_by(type) %>% 
  # pivot_wider(names_from = type, values_from = c(est, estimate)) %>% 
  gt::gt() %>% 
  data_color(
    columns = estimate,
    target_columns = everything(),
    fn = scales::div_gradient_pal(
      low = "darkblue", 
      mid = "white", 
      high = "red"
    ) %>% 
      {function(x) .(scales::rescale_mid(x, mid = 1))}
  ) %>% 
  cols_hide(columns = estimate) %>% 
  cols_label(term = "Zone",
             est = "OR (95% CI)",
             sig = "Significance") %>% 
  tab_header(title = "Unadjusted Zone Regressions, Stratified by CI",
             subtitle = "OR per 5 min in Zone")

```

```{r zones strat, adjusted}
## adjusted
res_hi = run_regression(temp_df_hi, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control,
               hemo_type = "zone")

res_lo = run_regression(temp_df_lo, 
               covariate_df = df, outcome = "bin_aki48h",
               hemo_type = "zone",
               covars_control = covars_control)

res_lo %>% 
  mutate(type = "CI < 2") %>% 
  bind_rows(res_hi %>% mutate(type = "CI >= 2")) %>% 
  mutate(est = glue::glue("{sprintf('%.2f', estimate)} ({sprintf('%.2f', lb)}, {sprintf('%.2f', ub)})"),
         sig = case_when(p.value < .01 ~ "***",
                         p.value < .01 ~ "**",
                         p.value < .05 ~ "*", 
                         p.value < .1 ~ ".",
                         .default = "")) %>% 
  select(term, type, est, estimate, sig) %>% 
  group_by(type) %>% 
  # pivot_wider(names_from = type, values_from = c(est, estimate)) %>% 
  gt::gt() %>% 
  data_color(
    columns = estimate,
    target_columns = everything(),
    fn = scales::div_gradient_pal(
      low = "darkblue", 
      mid = "white", 
      high = "red"
    ) %>% 
      {function(x) .(scales::rescale_mid(x, mid = 1))}
  ) %>% 
  cols_hide(columns = estimate) %>% 
  cols_label(term = "Zone",
             est = "OR (95% CI)",
             sig = "Significance") %>% 
  tab_header(title = "Adjusted Zone Regressions, Stratified by CI",
             subtitle = "OR per 5 min in Zone")
```


#### Zones (3) 

```{r zones 3 regression}
temp_df = 
  mapping %>% 
  select(id, contains("zone")) 

res_mult = run_regression(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control,
               hemo_type = "zone")

res_uni = run_regression(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               hemo_type = "zone", adjustment_type = "uni")

res_uni %>% 
  mutate(type = "unadjusted") %>% 
  bind_rows(res_mult %>% mutate(type = "adjusted")) %>% 
  mutate(est = glue::glue("{sprintf('%.2f', estimate)} ({sprintf('%.2f', lb)}, {sprintf('%.2f', ub)})"),
         sig = case_when(p.value < .01 ~ "***",
                         p.value < .01 ~ "**",
                         p.value < .05 ~ "*", 
                         p.value < .1 ~ ".",
                         .default = "")) %>% 
  select(term, type, est, estimate, sig) %>% 
  group_by(type) %>% 
  # pivot_wider(names_from = type, values_from = c(est, estimate)) %>% 
  gt::gt() %>% 
  data_color(
    columns = estimate,
    target_columns = everything(),
    fn = scales::div_gradient_pal(
      low = "darkblue", 
      mid = "white", 
      high = "red"
    ) %>% 
      {function(x) .(scales::rescale_mid(x, mid = 1))}
  ) %>% 
  cols_hide(columns = estimate) %>% 
  cols_label(term = "Zone",
             est = "OR (95% CI)",
             sig = "Significance") %>% 
  tab_header(title = "Zone Regressions",
             subtitle = "OR per 5 min in Zone")
```

```{r zones 3 strat and unadj}
## stratified and unadjusted

temp_df_lo = 
  mapping_cilow %>% 
  select(id, contains("zone")) 

temp_df_hi = 
  mapping_cihigh %>% 
  select(id, contains("zone")) 

res_hi = run_regression(temp_df_hi, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control,
               hemo_type = "zone",
               adjustment_type = "uni")

res_lo = run_regression(temp_df_lo, 
               covariate_df = df, outcome = "bin_aki48h",
               hemo_type = "zone", adjustment_type = "uni")

res_lo %>% 
  mutate(type = "CI < 2") %>% 
  bind_rows(res_hi %>% mutate(type = "CI >= 2")) %>% 
  mutate(est = glue::glue("{sprintf('%.2f', estimate)} ({sprintf('%.2f', lb)}, {sprintf('%.2f', ub)})"),
         sig = case_when(p.value < .01 ~ "***",
                         p.value < .01 ~ "**",
                         p.value < .05 ~ "*", 
                         p.value < .1 ~ ".",
                         .default = "")) %>% 
  select(term, type, est, estimate, sig) %>% 
  group_by(type) %>% 
  # pivot_wider(names_from = type, values_from = c(est, estimate)) %>% 
  gt::gt() %>% 
  data_color(
    columns = estimate,
    target_columns = everything(),
    fn = scales::div_gradient_pal(
      low = "darkblue", 
      mid = "white", 
      high = "red"
    ) %>% 
      {function(x) .(scales::rescale_mid(x, mid = 1))}
  ) %>% 
  cols_hide(columns = estimate) %>% 
  cols_label(term = "Zone",
             est = "OR (95% CI)",
             sig = "Significance") %>% 
  tab_header(title = "Unadjusted Zone Regressions, Stratified by CI",
             subtitle = "OR per 5 min in Zone")

```

```{r zones 3 strat, adjusted}
## adjusted
res_hi = run_regression(temp_df_hi, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control,
               hemo_type = "zone")

res_lo = run_regression(temp_df_lo, 
               covariate_df = df, outcome = "bin_aki48h",
               hemo_type = "zone",
               covars_control = covars_control)

res_lo %>% 
  mutate(type = "CI < 2") %>% 
  bind_rows(res_hi %>% mutate(type = "CI >= 2")) %>% 
  mutate(est = glue::glue("{sprintf('%.2f', estimate)} ({sprintf('%.2f', lb)}, {sprintf('%.2f', ub)})"),
         sig = case_when(p.value < .01 ~ "***",
                         p.value < .01 ~ "**",
                         p.value < .05 ~ "*", 
                         p.value < .1 ~ ".",
                         .default = "")) %>% 
  select(term, type, est, estimate, sig) %>% 
  group_by(type) %>% 
  # pivot_wider(names_from = type, values_from = c(est, estimate)) %>% 
  gt::gt() %>% 
  data_color(
    columns = estimate,
    target_columns = everything(),
    fn = scales::div_gradient_pal(
      low = "darkblue", 
      mid = "white", 
      high = "red"
    ) %>% 
      {function(x) .(scales::rescale_mid(x, mid = 1))}
  ) %>% 
  cols_hide(columns = estimate) %>% 
  cols_label(term = "Zone",
             est = "OR (95% CI)",
             sig = "Significance") %>% 
  tab_header(title = "Adjusted Zone Regressions, Stratified by CI",
             subtitle = "OR per 5 min in Zone")
```

#### Physiological Zones 

```{r bivar pzones}
temp_df = 
  pzones
  
res_mult = run_regression_biv(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control)

res_uni = run_regression_biv(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control, adjustment_type = "uni")

res_uni %>% 
  separate_wider_delim(term, delim = "_",
                       names = c("x", "map", "x2", "cvp")) %>% 
  mutate(cvp = sub("`.*", "", cvp)) %>% 
  mutate(sig = case_when(p.value < .01 ~ "***",
                         p.value < .01 ~ "**",
                         p.value < .05 ~ "*", 
                         p.value < .1 ~ ".",
                         .default = ""),
         lab = glue::glue("{sprintf('%.2f', estimate)} {sig}")) %>% 
  ggplot(aes(x = map, y = cvp, fill = estimate, label = lab)) +
  geom_tile(color = "black") +
  geom_text() +
  labs(x = "MAP", y = "CVP", title = "Fine Mapping, Unadjusted Models",
       subtitle = "OR Associated with 5 min Increase in Time in Range") +
  scale_fill_gradient2(low = "darkblue", mid = "white", high = "red", midpoint = 1, name = "Odds Ratio (OR)") +
  theme(legend.position = "none")

res_mult %>% 
  separate_wider_delim(term, delim = "_",
                       names = c("x", "map", "x2", "cvp")) %>% 
  mutate(cvp = sub("`.*", "", cvp)) %>% 
  mutate(sig = case_when(p.value < .01 ~ "***",
                         p.value < .01 ~ "**",
                         p.value < .05 ~ "*", 
                         p.value < .1 ~ ".",
                         .default = ""),
         lab = glue::glue("{sprintf('%.2f', estimate)} {sig}")) %>% 
  ggplot(aes(x = map, y = cvp, fill = estimate, label = lab)) +
  geom_tile(color = "black") +
  geom_text() +
  labs(x = "MAP", y = "CVP", title = "Fine Mapping, Adjusted Models",
       subtitle = "OR Associated with 5 min Increase in Time in Range") +
  scale_fill_gradient2(low = "darkblue", mid = "white", high = "red", midpoint = 1, name = "Odds Ratio (OR)") +
  theme(legend.position = "none") 

```


```{r bivar strat pzones uni}
# uniivariate 
temp_df = 
  pzones_hi 
res_mult_hi = run_regression_biv(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control,
               adjustment_type = "uni") %>% 
  mutate(type = "CI >= 2")

temp_df = 
  pzones_low %>% 
  select(id, contains("cvp") & contains("map"))
  
res_mult_lo = run_regression_biv(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control,
               adjustment_type = "uni") %>% 
  mutate(type = "CI < 2")

res_mult_hi %>% 
  bind_rows(res_mult_lo) %>% 
  separate_wider_delim(term, delim = "_",
                       names = c("x", "map", "x2", "cvp")) %>% 
  mutate(cvp = sub("`.*", "", cvp),
         # estimate = if_else(estimate > 10, NA, estimate),
         sig = case_when(p.value < .01 ~ "***",
                         p.value < .01 ~ "**",
                         p.value < .05 ~ "*", 
                         p.value < .1 ~ ".",
                         .default = ""),
         lab = glue::glue("{sprintf('%.2f', estimate)} {sig}")) %>% 
  ggplot(aes(x = map, y = cvp, fill = estimate, label = lab)) +
  geom_tile(color = "black") +
  geom_text() +
  labs(x = "MAP", y = "CVP", title = "Fine Mapping, Unadjusted Models, Stratified",
       subtitle = "OR Associated with 5 min Increase in Time in Range") +
  scale_fill_gradient2(low = "darkblue", mid = "white", high = "red", midpoint = 1, name = "Odds Ratio (OR)") +
  theme(legend.position = "none") +
  facet_grid(type ~ .)
```



```{r bivar strat pzones multi}
# multivariate 
temp_df = 
  pzones_hi 
res_hi = run_regression_biv(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control) %>% 
  mutate(type = "CI >= 2")

temp_df = 
  pzones_low 

res_lo = run_regression_biv(temp_df, 
               covariate_df = df, outcome = "bin_aki48h",
               covars_control = covars_control) %>% 
  mutate(type = "CI < 2")

res_hi %>% 
  bind_rows(res_lo) %>% 
  separate_wider_delim(term, delim = "_",
                       names = c("x", "map", "x2", "cvp")) %>% 
  mutate(cvp = sub("`.*", "", cvp),
         sig = case_when(p.value < .01 ~ "***",
                         p.value < .01 ~ "**",
                         p.value < .05 ~ "*", 
                         p.value < .1 ~ ".",
                         .default = ""),
         lab = glue::glue("{sprintf('%.2f', estimate)} {sig}")) %>% 
  ggplot(aes(x = map, y = cvp, fill = estimate, label = lab)) +
  geom_tile(color = "black") +
  geom_text() +
  labs(x = "MAP", y = "CVP", title = "Fine Mapping, Adjusted Models, Stratified",
       subtitle = "OR Associated with 5 min Increase in Time in Range") +
  scale_fill_gradient2(low = "darkblue", mid = "white", high = "red", midpoint = 1, name = "Odds Ratio (OR)") +
  theme(legend.position = "none") +
  facet_grid(type ~ .)
```



### Fine Mapping Analysis - All Zones at Once {.tabset}


#### Zones (5) 

```{r zones correlation}
temp_df = 
  mapping %>% 
  select(id, contains("shell")) %>% 
  rename_with(.cols = -id, ~sub("shell", "zone", .x))

cor_mat = 
  temp_df %>% 
  select(-id) %>% 
  cor(use = "na.or.complete", method = "pearson")

p_mat = ggcorrplot::cor_pmat(temp_df %>% 
  select(-id))

p1 = ggcorrplot(cor_mat,
           type = "lower",
           ggtheme = ggplot2::theme_light,
           show.diag = FALSE,
           lab = TRUE,
           title = "Unstratified",
           p.mat = p_mat,
           lab_size = 3) 

temp_df = 
  mapping_cihigh %>% 
  select(id, contains("shell")) %>% 
  rename_with(.cols = -id, ~sub("shell", "zone", .x))

cor_mat = 
  temp_df %>% 
  select(-id) %>% 
  cor(use = "na.or.complete", method = "pearson")

p_mat = ggcorrplot::cor_pmat(temp_df %>% 
  select(-id))


p2 = ggcorrplot(cor_mat,
           type = "lower",
           ggtheme = ggplot2::theme_light,
           show.diag = FALSE,
           lab = TRUE,
           title = "CI >= 2",
           p.mat = p_mat,
           lab_size = 3)

temp_df = 
  mapping_cilow %>% 
  select(id, contains("shell")) %>% 
  rename_with(.cols = -id, ~sub("shell", "zone", .x))

cor_mat = 
  temp_df %>% 
  select(-id) %>% 
  cor(use = "na.or.complete", method = "pearson")

p_mat = ggcorrplot::cor_pmat(temp_df %>% 
  select(-id))
  
p3 = ggcorrplot(cor_mat,
           type = "lower",
           ggtheme = ggplot2::theme_light,
           show.diag = FALSE,
           lab = TRUE,
           title = "CI < 2",
           p.mat = p_mat,
           lab_size = 3)


p1 + p3 + p2 + plot_layout(guides = "collect") + plot_annotation(title = "Pearson Correlations",
                                                                 caption = "X denotes p > .05")
```

```{r zones reg all}
temp_df = 
  mapping %>% 
  select(id, contains("shell")) %>% 
  rename_with(.cols = -id, ~sub("shell", "zone", .x)) %>% 
  left_join(df %>% select(id, bin_aki48h, all_of(covars_control)), by = "id") %>% 
  select(-id)

model = glm(bin_aki48h ~ ., data = temp_df, family = binomial())

# model %>% 
#   tbl_regression()
#   broom::tidy(exponentiate = TRUE) %>% 
#   gt()

  
temp_df = 
  mapping_cilow %>% 
  select(id, contains("shell")) %>% 
  rename_with(.cols = -id, ~sub("shell", "zone", .x)) %>% 
  left_join(df %>% select(id, bin_aki48h, all_of(covars_control)), by = "id") %>% 
  select(-id)

model_lo = glm(bin_aki48h ~ ., data = temp_df, family = binomial())

temp_df = 
  mapping_cihigh %>% 
  select(id, contains("shell")) %>% 
  rename_with(.cols = -id, ~sub("shell", "zone", .x)) %>% 
  left_join(df %>% select(id, bin_aki48h, all_of(covars_control)), by = "id") %>% 
  select(-id)

model_hi = glm(bin_aki48h ~ ., data = temp_df, family = binomial())

stargazer(model, model_lo, model_hi,
          column.labels=c("Overall","CI <2", "CI >= 2"), align=TRUE,
         type = "text")


```

```{r vif, eval = FALSE}
car::vif(model)
car::vif(model_lo)
car::vif(model_hi)
```

#### Zones (3) 

```{r zones 3 correlation}
temp_df = 
  mapping %>% 
  select(id, contains("zone"))

cor_mat = 
  temp_df %>% 
  select(-id) %>% 
  cor(use = "na.or.complete", method = "pearson")

p_mat = ggcorrplot::cor_pmat(temp_df %>% 
  select(-id))

p1 = ggcorrplot(cor_mat,
           type = "lower",
           ggtheme = ggplot2::theme_light,
           show.diag = FALSE,
           lab = TRUE,
           title = "Unstratified",
           p.mat = p_mat,
           lab_size = 3) 

temp_df = 
  mapping_cihigh %>% 
  select(id, contains("zone"))

cor_mat = 
  temp_df %>% 
  select(-id) %>% 
  cor(use = "na.or.complete", method = "pearson")

p_mat = ggcorrplot::cor_pmat(temp_df %>% 
  select(-id))


p2 = ggcorrplot(cor_mat,
           type = "lower",
           ggtheme = ggplot2::theme_light,
           show.diag = FALSE,
           lab = TRUE,
           title = "CI >= 2",
           p.mat = p_mat,
           lab_size = 3)

temp_df = 
  mapping_cilow %>% 
  select(id, contains("zone"))

cor_mat = 
  temp_df %>% 
  select(-id) %>% 
  cor(use = "na.or.complete", method = "pearson")

p_mat = ggcorrplot::cor_pmat(temp_df %>% 
  select(-id))
  
p3 = ggcorrplot(cor_mat,
           type = "lower",
           ggtheme = ggplot2::theme_light,
           show.diag = FALSE,
           lab = TRUE,
           title = "CI < 2",
           p.mat = p_mat,
           lab_size = 3)


p1 + p3 + p2 + plot_layout(guides = "collect") + plot_annotation(title = "Pearson Correlations",
                                                                 caption = "X denotes p > .05")
```

```{r zones 3 reg all}
temp_df = 
  mapping %>% 
  select(id, contains("zone")) %>% 
  left_join(df %>% select(id, bin_aki48h, all_of(covars_control)), by = "id") %>%
  select(-id)

model = glm(bin_aki48h ~ ., data = temp_df, family = binomial())

  
temp_df = 
  mapping_cilow %>% 
  select(id, contains("zone")) %>% 
  left_join(df %>% select(id, bin_aki48h, all_of(covars_control)), by = "id") %>%
  select(-id)

model_lo = glm(bin_aki48h ~ ., data = temp_df, family = binomial())

temp_df = 
  mapping_cihigh %>% 
  select(id, contains("zone")) %>% 
  left_join(df %>% select(id, bin_aki48h, all_of(covars_control)), by = "id") %>%
  select(-id)

model_hi = glm(bin_aki48h ~ ., data = temp_df, family = binomial())

stargazer(model, model_lo, model_hi,
          column.labels=c("Overall","CI <2", "CI >= 2"), align=TRUE,
         type = "text")


```

```{r vif2, eval = FALSE}
car::vif(model)
car::vif(model_lo)
car::vif(model_hi)
```

#### Physiological Zones

```{r pzones 3 correlation}
temp_df = 
  pzones %>% 
  magrittr::set_colnames(c("id", "lo map lo cvp", "lo map hi cvp", "hi map lo cvp", "hi map hi cvp"))

cor_mat = 
  temp_df %>% 
  select(-id) %>% 
  cor(use = "na.or.complete", method = "pearson")

p_mat = ggcorrplot::cor_pmat(temp_df %>% 
  select(-id))

p1 = ggcorrplot(cor_mat,
           type = "lower",
           ggtheme = ggplot2::theme_light,
           show.diag = FALSE,
           lab = TRUE,
           title = "Unstratified",
           p.mat = p_mat,
           lab_size = 3) 

temp_df = 
  pzones_hi %>% 
  magrittr::set_colnames(c("id", "lo map lo cvp", "lo map hi cvp", "hi map lo cvp", "hi map hi cvp"))


cor_mat = 
  temp_df %>% 
  select(-id) %>% 
  cor(use = "na.or.complete", method = "pearson")

p_mat = ggcorrplot::cor_pmat(temp_df %>% 
  select(-id))


p2 = ggcorrplot(cor_mat,
           type = "lower",
           ggtheme = ggplot2::theme_light,
           show.diag = FALSE,
           lab = TRUE,
           title = "CI >= 2",
           p.mat = p_mat,
           lab_size = 3)

temp_df = 
  pzones_low %>% 
  magrittr::set_colnames(c("id", "lo map lo cvp", "lo map hi cvp", "hi map lo cvp", "hi map hi cvp"))


cor_mat = 
  temp_df %>% 
  select(-id) %>% 
  cor(use = "na.or.complete", method = "pearson")

p_mat = ggcorrplot::cor_pmat(temp_df %>% 
  select(-id))
  
p3 = ggcorrplot(cor_mat,
           type = "lower",
           ggtheme = ggplot2::theme_light,
           show.diag = FALSE,
           lab = TRUE,
           title = "CI < 2",
           p.mat = p_mat,
           lab_size = 3)


p1 + p3 + p2 + plot_layout(guides = "collect") + plot_annotation(title = "Pearson Correlations",
                                                                 caption = "X denotes p > .05")
```

```{r pzones reg all}
temp_df = 
  pzones %>% 
  left_join(df %>% select(id, bin_aki48h, all_of(covars_control)), by = "id") %>%
  select(-id)

model = glm(bin_aki48h ~ ., data = temp_df, family = binomial())

  
temp_df = 
  pzones_low %>% 
  left_join(df %>% select(id, bin_aki48h, all_of(covars_control)), by = "id") %>%
  select(-id)

model_lo = glm(bin_aki48h ~ ., data = temp_df, family = binomial())

temp_df = 
  pzones_hi %>% 
  left_join(df %>% select(id, bin_aki48h, all_of(covars_control)), by = "id") %>%
  select(-id)

model_hi = glm(bin_aki48h ~ ., data = temp_df, family = binomial())

stargazer(model, model_lo, model_hi,
          column.labels=c("Overall", "CI <2", "CI >= 2"), align=TRUE)
         


```

```{r vif3, eval = FALSE}
car::vif(model)
car::vif(model_lo)
car::vif(model_hi)
```

